Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-04-03 manuscript/manuscript.Rmd
Added table processor.

First we draw $m_d=100000$ random asymmetric generalised normal distributions, parametrised as above. As before, for each distribution, up to $10 \%$ of instances are replaced by outlier values, and this is repeated $10$ times. We then compute residuals after optimising robust shift-sensitive transformations with the empirical tapered cosine weighting method.

@@

```{r goodness-of-fit-1, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Residual error as a function of empirical probability. ",
  "Percentiles of the error are shown for robust, shift-sensitive transformations of 100000 randomly drawn asymmetric ",
  "generalised normal distributions, with 10 randomly drawn outliers distributions, ",
  "(up to 10% of samples) each. Larger errors occur for more extreme values at the edges of each distribution. ",
  "For comparison, the 99th percentile of residual errors for transformations of outlier-free distributions are shown (grey dashed line).")

@@

@@

The second error,

>>>>

First we draw $m_d=10000$ random asymmetric generalised normal distributions, parametrised as above. As before, for each distribution, up to $10 \%$ of instances are replaced by outlier values, and this is repeated $10$ times. We then compute residuals after optimising robust shift-sensitive transformations with the empirical tapered cosine weighting method.

@@

```{r goodness-of-fit-1, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Residual error as a function of empirical probability. ",
  "Percentiles of the error are shown for robust, shift-sensitive transformations of 10000 randomly drawn asymmetric ",
  "generalised normal distributions, with 10 randomly drawn outliers distributions, ",
  "(up to 10% of samples) each. Larger errors occur for more extreme values at the edges of each distribution. ",
  "For comparison, the 99th percentile of residual errors for transformations of outlier-free distributions are shown (grey dashed line).")

@@

```
```{r include = FALSE, eval = FALSE}
data <- .get_test_statistic_data(manuscript_dir = manuscript_dir)

@@
